The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Add script to calculate bigrams and trigrams

# # wip function ngrams
# get_ngrams <- function(df, n) {
#   if (!is.numeric(n)) {
#     stop("n is not numeric")
#   }
#   emu_theses %>%
#     mutate(author = paste(first_name, last_name)) %>% 
#     select(author, title, text, -c(year, first_name, last_name, text_start, text_end)) %>% 
#     unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
#     separate(bigram, into = c("first","second"), sep = " ", remove = FALSE) %>%
#     anti_join(stop_words, by = c("first" = "word")) %>%
#     anti_join(stop_words, by = c("second" = "word")) %>%
#     anti_join(stop_words_custom, by = c("first" = "word")) %>%
#     anti_join(stop_words_custom, by = c("second" = "word")) %>%
#     filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
#     filter(first != second) %>% 
#     filter(first != "source")
# }
# emu_theses_ngrams <- get_ngrams(emu_theses, 2)

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

emu_theses_bigrams_separated <- emu_theses_bigrams |>  
  separate(bigram, into = c("first","second"), sep = " ", remove = FALSE)

emu_theses_bigrams_filtered <- emu_theses_bigrams_separated |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word"))

bigram_counts <- emu_theses_bigrams_filtered |> 
  count(first, second, sort = TRUE)

@@

  # # filter(str_detect(first, "[a-z]") & str_detect(second, "[a-z]")) %>% 
  # filter(first != second) %>% 
  # filter(first != "source")

>>>>

## TO DO: generalise bigrams and trigrams into an ngrams function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  separate(bigram, into = c("first", "second"), sep = " ", remove = FALSE) |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word")) |> 
  filter(str_detect(first, "[a-z]") & 
         str_detect(second, "[a-z]"))

bigram_counts <- emu_theses_bigrams |> 
  count(first, second, sort = TRUE)

@@

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) |> 
  separate(trigram, into = c("first", "second", "third"), sep = " ", remove = FALSE) |> 
  filter(!first %in% stop_words$word,
         !second %in% stop_words$word,
         !third %in% stop_words$word) |>  
  filter(str_detect(first, "[a-z]"), 
         str_detect(second, "[a-z]"),
         str_detect(third, "[a-z]"))

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, sort = TRUE)

trigram_counts

# Bigram tf-idf
bigram_tf_idf <- emu_theses_bigrams |> 
  count(title, bigram) |> 
  bind_tf_idf(bigram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf

# Trigram tf-idf
trigram_tf_idf <- emu_theses_trigrams |> 
  count(title, trigram) |> 
  bind_tf_idf(trigram, title, n) |> 
  arrange(desc(tf_idf))

trigram_tf_idf
